Ejemplificando art

### 2024-02-24 notebooks/example_script.Rmd
Adds html output to Mario's notebook

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output:
  word_document:
    fig_width:  6
    fig_height: 6
editor_options:
  markdown:
    canonical: true
---

>>>>

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output:
  word_document:
    fig_width:    6
    fig_height:   6
  html_document:
    fig_width:    6
    fig_height:   6
    code_folding: hide
    toc:          yes
    toc_float:    yes
editor_options:
  markdown:
    canonical:    false
---
